\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

{Teaching Algorithmic Game Theory with Programming Competitions}

{Andrew Wonnacott}

{COS 398 IW 09 (Professor Walker)}

\begin{itemize}
\tightlist
\item
  {Abstract}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Framing: Developing A Modular Framework for Developing, Deploying,
  and Evaluating programming Assignments in a theory course}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Introduction 1.5}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {goal}{~(1st par) - helping improve the quality of theory eduction for
  broader cs majors - what will I contribute?}
\item
  {motivation - currently there is a lot of work repeated every year,
  and with very little knowledge preserved (institutional memory), which
  takes up CS dept resources. Lots of tasks could be automated. Personal
  motivation: enjoyed the course, especially these assignments}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Problem Background / related work}{~- past years, harvard, 4.5}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Related work: this course has had programming assignments for years}
\item
  {Related work: 126/226 have automated all of this for years}
\item
  {Related work: Harvard also has AGT PA games (nobody else does)}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {approach - big picture? 3 \textless{}- {[}1-8{]}}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Design of my solution, how it differs}
\item
  {Introduce present / future split}
\item
  {Design and implementation of assignments / design and implementation
  of frameworks for implementing assignments}
\item
  {product component overview}
\item
  {- iterate, provide resources}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Implementation - details important to achieving goal. Keys to
  success. How+why 10}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {~- language choice}
\item
  {sharing code between tesitng / leaderboard / submit / grader (focus
  on modularity)}
\item
  {Sharing code between programming assignments to make new assignment
  development easier}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Evaluation 5.5}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {results - current use in 445}
\item
  {Use next year in 445}
\item
  {Performance evaluation by user studies}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Student reviews}
\item
  {Grader reviews (myself, Matt)}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Conclusions 1.25}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {What will I have to do next year that I didn't have to do this year?}
\item
  {What will I have to repeat next year?}
\item
  {What would I need to tell someone so they would know how ot do this?}
\item
  {future work - next year}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Bibliography}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {Collaboration with Matt to co-write the programming assignment specs
  I would be following during `present' work}
\item
  {Note I was paid for some of my time grading (included copying grades
  around when I hadn't finished some of the formatting in the
  autograder, but not developing the autograder)}
\item
  {acknowledgements - thanks matt, cyril, dave, other students in my
  seminar, students in course, UCAs and grad students}
\end{itemize}

\begin{itemize}
\tightlist
\item
  {}
\end{itemize}

{}

{Introduction~~~~~~~~}

{Professor Weinberg's COS 445 (Economics and
Computing)}\textsuperscript{\protect\hyperlink{ftnt1}{{[}1{]}}}{~taught
Spring 2017 was one of the most popular theory classes this department
has ever
taught.}\textsuperscript{\protect\hyperlink{ftnt2}{{[}2{]}}}{~Despite
its classification as a `theory' distribution, the course contains
several programming challenges. In these assignments, students to apply
theoretical results on iterated games and auctions to design and
implement strategies which play iterated games or participate in
auctions. The submissions are then tested against each other and against
instructor strategies. Student feedback emphasized the role of the
programming exercises in the popularity of the
course.}\textsuperscript{\protect\hyperlink{ftnt3}{{[}3{]}}}{~However,
only two of the eight problem sets contained programming exercises in
Spring 2017, and course instructors expressed interest in having a
similar exercise in each problem set. The goal of my project is to
develop new assignments in the same form which develop theoretical
understanding of other topics covered in algorithmic game theory, to
expand the resources available to students completing these assignments,
and to improve the tooling used by instructors for grading student
submissions for these assignments. }

{Problem Background and Related Work}

{This work will be heavily based on the two programming exercises most
recently maintained by Cyril Zhang in Spring 2017, described above,
which I completed while enrolled in this course in that semester. These
assignments, as with those I develop, are written in Java, as dictated
by the prerequisites of the course. Similar assignments have been
developed for Harvard's course by the same
title,}\textsuperscript{\protect\hyperlink{ftnt4}{{[}4{]}}}{~in which
students develop a BitTorrent simulation and auction bidding agents in
Python. However, a brief survey of courses in algorithmic game theory at
other universities, including
Stanford}\textsuperscript{\protect\hyperlink{ftnt5}{{[}5{]}}}{,
Cornell}\textsuperscript{\protect\hyperlink{ftnt6}{{[}6{]}}}{, U.
Washington}\textsuperscript{\protect\hyperlink{ftnt7}{{[}7{]}}}{,
Yale}\textsuperscript{\protect\hyperlink{ftnt8}{{[}8{]}}}{,
Penn}\textsuperscript{\protect\hyperlink{ftnt9}{{[}9{]}}}{, Georgia
Tech}\textsuperscript{\protect\hyperlink{ftnt10}{{[}10{]}}}{, Carnegie
Mellon}\textsuperscript{\protect\hyperlink{ftnt11}{{[}11{]}}}{,
Duke}\textsuperscript{\protect\hyperlink{ftnt12}{{[}12{]}}}{, found no
other results.}

{~~~~~~~~Because of the urgent need for an assistant who can program and
maintain the existing programming challenges for the current semester,
Professor Weinberg and I decided to use the developed assignments
directly as a component of the Spring 2018 instance of COS 445. Thus, I
have a unique opportunity to organize my independent work around live
student feedback, which will be incorporated into the development of
later assignments.}

{~~~~~~~~Potential assignment topics include college admissions (using
stable matchings), elections, and blockchain incentives. The design of
the assignments and instructor solutions will be done under supervision
and lead of Professor Weinberg: we will both brainstorm potential
assignments, and then select for implementation the one we think best
engages students. I will be primarily responsible for developing the
software interfaces for students to design against, the instructor
tooling for quantitative and qualitative evaluation of student
submissions, and the student tooling for simulating and testing their
assignments. The student tooling will allow students to test their
programs in assignments which simulate the real evaluation environment.
I will also be providing support to students who are completing the
assignments and organizing the usage of the instructor evaluation tools.
If time permits, I would like to develop an online leaderboard connected
to the CS Dropbox to allow students to compare their submissions against
each other in real time before the submission deadline.}

{Evaluation}

{I will request feedback from current students about their overall
satisfaction with the programming assignments as compared to additional
theoretical problems (which are still the assignment backbone), their
usage of my tools, and their general suggestions, to improve subsequent
assignments. I will also request feedback from Professor Weinberg and
the undergraduate graders of the course regarding how to provide better
instructor-side tooling for the assignments. My success will be valuable
through students' self-perceived ability to focus on the core assignment
content without experiencing undue difficulties with the assignment
structure and through instructors' present and future usage of the
developed ~assignments. Qualitative measures of success include elements
of survey results described above, decrease in illegal (i.e. errors
unrelated to course content) programs submitted as measured by
anonymized metrics such as lower-outlier rates in quantitative
simulation performance of student submissions, and decrease in
instructor resources (e.g. time) required to maintain and grade the
assignments. These data can be compared to similar data from the two
similar exercises assigned in previous years.}

{Big mistake in `present' - bad at communicating how students would be
graded}

{In the first three weeks of the semester, I have already developed,
implemented, and deployed two assignments, and have developed all of the
tools necessary for grading submissions. I am currently collecting the
completed tools into one automated script which will be able to produce
collated student results and to aggregate results into graphics for
presentation. Preliminary data suggests that rate of illegal submissions
has dropped dramatically with the availability to students of improved
testing software.}

{}

{}

{Framing:}

{-design assignments vs building assignment infrastructure}

{- present vs future}

{-'do it, do it right, do it again' (modularity, extensibility,
reusability)}

{-Components: student testing script, dropbox testing script,
leaderboard script, grader script, sample strategies, instructor
strategies. 4/6 reuasable}

{How are the programming assignments graded? Why were we not informed of
how they would be graded for the first two problem sets?}

{Here is a link to the grading policies sheet for programming
assignments: GradesForProgramming.pdf. This document was in the General
Resources section of the Piazza resources page, referred to from the
programming assignment description for both problem sets (although the
reference was confusing). Survey results indicate that we didn't
properly advertise it and most students were not aware of its existence.
Thus, a lot of students were surprised that the objective questions and
the strength of the writeup were the dominant factors in their grades
-\/-\/- not the performance of their software. Given that we did a poor
job making this clear, we'll be altering how these two assignments are
included in your final grade. See @394 for details.}

{What is the role of programming in a theory course?}

{Survey results indicate at least a few students are confused why they
need to program in a theory course. One key difference between COS 445
(being a theoretical computer science course on game theory) and ECO
418, MAT 378, or POL 347 (other game theory courses offered at
Princeton) is that we place some emphasis on the connections between
game-theoretic results and algorithms, software, and other aspects of
computer science. One way in which we do this is by asking students to
connect their learning in this course to their learning in prerequisite
courses, in this case COS 226. Past course feedback was overwhelmingly
positive for programming challenges (so the hope is that the initial
negative feedback this cycle is due more to poor administration)}

{Here's what we didn't make clear: the "programming assignments" aren't
really about your ability to code. They are about placing the
theoretical results from the course in context. They create a scenario
in which mastery of theoretical results from the course content is
demonstrated by making and justifying real-world decisions. However (and
we didn't communicate this well), we are still grading your response to
the programming exercises as a theory problem. That is why 2/3 of the
credit on the "programming exercises" goes to the theoretical questions,
and why poor performance of your software strategy (so long as it does
not crash) can be entirely offset by a well-written writeup. So, in
actuality, 0\% of your grade is solely dependent on your programming
ability -\/-\/- as is appropriate in a theory course! We include the
empirical performance of your strategy in a way that can only benefit
your grade in the course, to reward students who demonstrated mastery of
the course content by designing a great strategy even if they did not
describe it perfectly}

{Why do we have to use Java (not Python)?}

{We would love to do these assignments in Python, as many students
requested, but unfortunately we do not have Python experience as a
course prerequisite and are firmly of the conviction that it is
inappropriate for a course to expect students to learn a programming
language they have never seen before with no formal instruction (no
matter how many other courses do that).}

{Additionally, empirical data from other course surveys suggests that
90\% of students report themselves fluent in Java after the Princeton
introductory sequence, compared to 30\% for python.}

{Why are my strategies graded against instructor strategies instead of
against the strategies of my peers?}

{We do not believe it is right to grade students against their peers'
submissions because academic performance should not be a zero-sum game.
This was overwhelmingly requested by last year's class.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\protect\hyperlink{ftnt_ref1}{{[}1{]}}{~}{\href{https://www.google.com/url?q=https://www.cs.princeton.edu/~smattw/Teaching/cos445sp17.htm\&sa=D\&ust=1522867200381000}{https://www.cs.princeton.edu/\textasciitilde{}smattw/Teaching/cos445sp17.htm}}

\protect\hyperlink{ftnt_ref2}{{[}2{]}}{~}{\href{https://www.google.com/url?q=https://www.princetoncourses.com/course/1174012095\&sa=D\&ust=1522867200381000}{https://www.princetoncourses.com/course/1174012095}}

\protect\hyperlink{ftnt_ref3}{{[}3{]}}{~Ibid.}

\protect\hyperlink{ftnt_ref4}{{[}4{]}}{~}{\href{https://www.google.com/url?q=https://beta.blogs.harvard.edu/k108875/assignments/\&sa=D\&ust=1522867200386000}{https://beta.blogs.harvard.edu/k108875/assignments/}}

\protect\hyperlink{ftnt_ref5}{{[}5{]}}{~}{\href{https://www.google.com/url?q=https://theory.stanford.edu/~tim/364a.html\&sa=D\&ust=1522867200382000}{https://theory.stanford.edu/\textasciitilde{}tim/364a.html}}

{\href{https://www.google.com/url?q=https://theory.stanford.edu/~tim/f16/f16.html\&sa=D\&ust=1522867200382000}{https://theory.stanford.edu/\textasciitilde{}tim/f16/f16.html}}

\protect\hyperlink{ftnt_ref6}{{[}6{]}}{~}{\href{https://www.google.com/url?q=https://www.cs.cornell.edu/courses/cs6840/2014sp/\&sa=D\&ust=1522867200383000}{https://www.cs.cornell.edu/courses/cs6840/2014sp/}}

\protect\hyperlink{ftnt_ref7}{{[}7{]}}{~}{\href{https://www.google.com/url?q=https://courses.cs.washington.edu/courses/cse522/05sp/\&sa=D\&ust=1522867200383000}{https://courses.cs.washington.edu/courses/cse522/05sp/}}

\protect\hyperlink{ftnt_ref8}{{[}8{]}}{~}{\href{https://www.google.com/url?q=https://zoo.cs.yale.edu/classes/cs455/fall11/\&sa=D\&ust=1522867200384000}{https://zoo.cs.yale.edu/classes/cs455/fall11/}}

\protect\hyperlink{ftnt_ref9}{{[}9{]}}{~}{\href{https://www.google.com/url?q=https://www.cis.upenn.edu/~aaroth/courses/agtS15.html\&sa=D\&ust=1522867200384000}{https://www.cis.upenn.edu/\textasciitilde{}aaroth/courses/agtS15.html}}

\protect\hyperlink{ftnt_ref10}{{[}10{]}}{~}{\href{https://www.google.com/url?q=https://web.archive.org/web/20131002121909/http://www.cc.gatech.edu/\%257Eninamf/LGO10/index.html\&sa=D\&ust=1522867200384000}{https://web.archive.org/web/20131002121909/http://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}}

\protect\hyperlink{ftnt_ref11}{{[}11{]}}{~}{\href{https://www.google.com/url?q=http://www.cs.cmu.edu/~arielpro/15896s16/index.html\&sa=D\&ust=1522867200385000}{http://www.cs.cmu.edu/\textasciitilde{}arielpro/15896s16/index.html}}

\protect\hyperlink{ftnt_ref12}{{[}12{]}}{~}{\href{https://www.google.com/url?q=https://www2.cs.duke.edu/courses/spring16/compsci590.4/\&sa=D\&ust=1522867200385000}{https://www2.cs.duke.edu/courses/spring16/compsci590.4/}}

\end{document}
